---
title: "Multiple Linear Regrssion"

output:
  html_document: default
  html_notebook: default
---

***Before building model we will check:***

- ***Descriptive statistic of the dataset***
 
- ***Find correlation***
 
- ***Check association between variables with the help of scatter plot.***
 
- ***Build Multiple Linear Regression model.***
 
- ***Perform Residual Analysis on the best model (Plot and Normality Test- Shapiro's-Wilk)***


#### Loading R-packages
```{r}
library(corrplot)
```

#### Import dataset
```{r}
mydata = read.table("C:/Users/Supriya Khadake/Desktop/Spring_2017/527/HW/HW4/HW4_DATA.txt", header = T)

# Assigning variablels
sales = mydata$sales
title = mydata$title
footage = mydata$footage
pc = mydata$pc
apple = mydata$apple

#Check first few rows of the dataset
head(mydata)

# Descriptive statistic 
summary(mydata)
```

#### Scatter Plot to check association between variables
From the below plots we can see that there is a linear association between variables
```{r}
plot(mydata)
```

#### Lets check correlation between variables
From the below plot we can see that title and pc, and title ana apple have strong correlation
```{r}
correlation = cor(cbind(sales, title, footage, pc, apple))
corrplot(correlation, method = "number")
```

#### Lets proceed and build regression model
```{r}
model1 = lm(sales ~ title + footage +  pc + apple)
summary(model1)
```

By individual parameter test we can say that none variable is significant to the variable sales
Hence we eliminate one by one and rebuild th model

#### Rebuilding model by eliminating apple
```{r}
model2 = lm(sales ~ title + footage +  pc)
summary(model2)
```

#### Rebuilding model by eiminating pc
```{r}
model3 = lm(sales ~ title + footage)
summary(model3)
```

#### Rebuilding model by eiminating footage
```{r}
model4 = lm(sales ~ title)
summary(model4)
```


#### Residual Analysis
1. We can see Constant Variance
2. It shows Linearity distribution as points are scattered around zero line
3. Normality Test: p-value > 0.05 hence we accept NULL hypothesis
4. Influential Points: Potential outliers are observed with residual/studentized residuals larger than 3 and smaller than -3. We observe that one potential outlier in this case

```{r}
plot(fitted(model1), rstandard(model1), main = "Predicted vs Residuals")
abline(a = 0, b = 0, col = "red")

r = rstandard(model1)
shapiro.test(r)
```

